Titeln på avhandlingens språk

### 2022-09-01 model.tex
values

We begin by discretizing normalized neuroticism into \emph{low} and \emph{high} ranges, \( [0.0, 0.5) \) and \( [0.5, 1.0] \) respectively. 
We also bin \ac{TTF} into three ranges by splitting the data on the 3-quantiles; we will refer to these ranges of \ac{TTF} as \emph{low}, \emph{medium}, and \emph{high impairment}.

@@

Finally, we assign a number to each sample corresponding to \emph{how long} the current combination of level of impairment and transition has been in effect, in number of steps.
This count resets whenever this combination changes.
This value is subsequently discretized into bins with edges \( [0, 5) \), \( [5, 10) \), and \( [10, \infty) \); we will refer to these discretized levels as \emph{short}, \emph{medium}, and \emph{long duration}, respectively.

>>>>

\begin{table}[]
\centering
\caption{Default bins used for model parameter levels.}
\label{tab:defaultbins}
% \resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Parameter} & \textbf{Low}     & \textbf{Medium}      & \textbf{High}         \\ \midrule
Neuroticism        & \( [0, 0.5) \)   &                      & \( [0.5, 1.0] \)      \\
Impairment         & \( [0, 1.482) \) & \( [1.482, 3.198) \) & \( [3.198, \infty) \) \\
Duration           & \( [0, 5) \)     & \( [5, 10) \)        & \( [10, \infty) \)    \\ \bottomrule
\end{tabular}%
% }
\end{table}

We begin by discretizing normalized neuroticism into \emph{low} and \emph{high} ranges, and \ac{TTF} into three ranges by splitting the data on the 3-quantiles; we will refer to these ranges of \ac{TTF} as \emph{low}, \emph{medium}, and \emph{high impairment}.
\cref{tab:defaultbins} shows the exact values used for these ranges.

@@

Finally, we assign a number to each sample corresponding to \emph{how long} the current combination of level of impairment and transition has been in effect, in number of steps.
This count resets whenever this combination changes.
This value is subsequently discretized into three levels; \emph{short}, \emph{medium}, and \emph{long duration} (again, refer to \cref{tab:defaultbins} for the exact values used).
